\Huge \scshape \fontfamily{pbk}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \large An Example of the dndbook Class

### 2021-08-12 example.tex
Added a "listparagraph" type that outputs a bolded title with hanging-indent text, used in class features, background options, etc
Reverted default author for consistency with upstream
Expanded the example for the listparagraph format option.

\title{
  \Huge \scshape \fontfamily{pbk}\selectfont
  The Dark \LaTeX{} \\
  \medskip
  \normalfont
  \large
  An Example of the dndbook Class
}
\author{The rpgTeX Team \and Steve}
\date{}

@@

\listparagraph[6pt]{Listparagraph}
{The listparagraph format allows hanging indented lists of options, such as those
used for class features and background skill/tool proficiency options.}

\listparagraph{Listparagraph}
{The listparagraph with no vertical space after the previous paragraph.}

>>>>

\title{
  \Huge \scshape \fontfamily{pbk}\selectfont
  The Dark \LaTeX{} \\
  \medskip
  \normalfont
  \large
  An Example of the dndbook Class
}
\author{The rpgTeX Team}
\date{}

@@

\subsubsection{Hanging Indent Features}
The |listparagraph| format allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

\listparagraph[6pt]{Doors}
{The doors are made from thick lumber and are unlocked.}

\listparagraph{Light}
{The area is illuminated by candles placed in sconces on the
walls. Each candle has had a \textit{continual flame} spell
cast on it. Dispelling a flame is rumoured to give grievous offence
to the host.}

\listparagraph{Ventilation}
{All areas contain an adequate air supply. The air is renewed
via lung-like sacks that cling to the ceiling.}
